### 2024-03-15 sections/4gluing.tex
cref -> Cref

Given a stratified manifold $M$, we defined the $\infty$-category of locally constant factorization algebras on it $\lcfa_M (\catC)$. We want to examine what we can say about the behavior of this $\infty$-category under collar-gluings in the manifold variable. Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \cref{thm:disk_alg=lcfa} there is no loss at all.

@@

\begin{corollary}\label{cor:fbar_func_discrete}
    Taking only the first part of the proof of \cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
    \end{equation}
    %
    that is an algebra.
\end{corollary}

@@

\begin{proof}[Proof of \cref{thm:gluing_alg_disk/M}]
    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \cref{def:collar-gluing}. This can be used to construct the cospan of restriction functors $\alg{\disk_{/M_-}} (\catC) \rightarrow \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk_{/M_+}} (\catC)$. Using this data we can define the pullback $\infty$-category
    %
    \begin{equation}
        \mathscr{P} := \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
    %
    The further open embeddings of $M_-$, $M_0 \times \mathbb{R}$ and $M_+$ into $M$ again give rise to restriction functors that form a commutative square
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[r] \arrow[d] & \alg{\disk_{/M_+}} (\catC) \arrow[d] \\
            \alg{\disk_{/M_-}} (\catC) \arrow[r] & \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC),
        \end{tikzcd}
    \end{equation}
    %
    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$. Our job is to find an inverse to this functor.

    Consider the following construction. Given the data of an object $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$. We do this by relying on factorization homology and the bar construction. Given $(U \xhookrightarrow{} M) \in \disk_{/M}$ we define
    %
    \begin{equation}\label{eq:def_of_A_in_proof}
        A(U) := \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
    \end{equation}
    %
    where $U_-$, $U_0$ and $U_+$ are defined through the inherited collar-gluing $U \xhookrightarrow{} M \xrightarrow{} [-1,1]$. Well-definition of the bar construction is provided if we have the appropriate left and right module structures on $\int_{U_-} A_-$ and $\int_{U_+} A_+$ over the associative algebra $\int_{U_0 \times \mathbb{R}} A_0$. Pushforward along the restrictions $f|_{U_-}: U_- \rightarrow \left[-1, 1\right)$ and $f|_{U_+}: U_+ \rightarrow \left(-1, 1\right]$, together with the properties of factorization homology provides these left and right module structures. Furthermore, the associative algebra object is exactly the appropriate one since consecutive restrictions commute on the nose. The above argument is essentially the statement that there is a functor
    %
    \begin{align}
        \gamma: \mathscr{P} \xrightarrow{\ \ \int \ \ } &\alg{\mfld_{/M_-}}(\catC) \bigtimes\limits_{\alg{\mfld_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\mfld_{/M_+}} (\catC)\notag\\ &\xrightarrow{\ - \circ \bar{f} \ } \mathsf{Fun}(\mfld_{/M}, \alg{\mathsf{Assoc^{RL}}} (\catC)) \xrightarrow{\ \mathsf{B} \circ - \ } \mathsf{Fun}(\mfld_{/M},\catC) \xrightarrow{\ } \mathsf{Fun}(\disk_{/M}, \catC),
    \end{align}
    %
    where $\bar{f}$ is the functor from \cref{lem:fbar_func}.

    Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk_{/M}, \catC)$. Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \cref{lem:B_sym_mon} for the latter), together with \cref{lem:fbar_func} that lends this property to $\bar{f}$. With that we have constructed a functor
    %
    \begin{equation}
        \gamma : \mathscr{P} \xrightarrow{\ \ \ \ } \alg{\disk_{/M}} (\catC).
    \end{equation}

@@

    Finally, we want to show that $\rho$ is fully faithful, i.e. we want to show that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$. That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms. Nothing new happens in the calculations involving restrictions that don't involve multiple pieces, since their logic essentially only depends on the properties of the bar construction when restricting. In the rest of the calculations we crucially used the collar-gluing property of factorization homology. That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \cref{rem:fh_pushforward_functorial}. Namely, these provide equivalences of functors
    %
    \begin{equation}
        \int_U - \simeq \int_{[-1,1]} (f|_U)_* - \simeq \mathsf{B} \circ (f|_U)_* = \int_{U_-} (-)_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} (-)_0} \int_{U_+} (-)_+,
    \end{equation}
    %
    which is exactly the collar-gluing property extended to the level of morphisms.
\end{proof}

Together with \cref{thm:disk_alg=lcfa} we immediately have the following corollary:

@@

Taking into account \cref{cor:disk_alg=falg} together with \cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.

@@

\begin{example}\label{ex:reproduce_lcfas_on_interval}
    With the ingredients we have introduced up to now, specifically in \cref{ssec:lcfa_on_ints}, we can do a nontrivial check of the gluing theorem. This is because we can write a collar-gluing of the closed interval $[-1,1] \cong \left[-1,1\right) \coprod_{(-1,1)} \left(-1,1\right] \cong \mathbb{R}_{\geq 0} \coprod_{\mathbb{R}} \mathbb{R}_{\leq 0}$. We note here that we have written $\mathbb{R}_{\leq 0}$ and $\mathbb{R}_{\geq 0}$ to emphasize the maps forming the decomposition. At the level of unstructured objects these two are isomorphic (see also \cref{rem:left_or_right_module}). For this example, the theorem says that locally constant factorization algebras on the closed interval should be given by
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \simeq \lcfa_{\mathbb{R}_{\geq 0}} (\catC) \bigtimes_{\lcfa_{\mathbb{R}} (\catC)} \lcfa_{\mathbb{R}_{\leq 0}} (\catC) \simeq \mathsf{RMod} (\catC) \bigtimes_{\alg{\mathbb{E}_1} (\catC)} \mathsf{LMod} (\catC),
    \end{equation}
    %
    where the functors are the ones that forget the module. At the level of objects, this is the data of an algebra with a right module $(A, R) \in \mathsf{RMod} (\catC)$ and an algebra with a left module $(B, L) \in \mathsf{LMod} (\catC)$, such that the algebras are equal $A = B$. But this is exactly the same as the description we gave in terms of an algebra with a left and a right module, i.e. an algebra over $\mathsf{Assoc^{RL}}$, in \cref{cor:lcfas_on_closed_int}.
\end{example}

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    A highly nontrivial check of the gluing theorem is given by the circle $S^1$. Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. This result is not generalizable to higher spheres because it uses the technology of covering spaces. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Unlike the covering space result for the circle \cite[sec.5.5]{ginot2015} which doesn't generalize to higher spheres, the gluing theorem has no such restriction. Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

@@

\begin{example}\label{ex:cylinder_mobius_band}
    In \cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \cref{prop:exp_of_products_lc} together with the results of \cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$. The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist. Using the notation from \cref{ex:reproduce_lcfas_on_S1} the diagram becomes
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1^{\mathsf{op_f}} \arrow[r, phantom, "\simeq", description] & B^{\mathsf{op_f}} \\
            A \arrow[ru, phantom, "\simeq", sloped, description] \arrow[rd, phantom, "\simeq", sloped, description] & & & \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 \arrow[r, phantom, "\simeq", description] & B,
        \end{tikzcd}
    \end{equation}
    %
    where $^{\mathsf{op_f}}$ is the opposite functor in the fiber direction. Thus, instead of an $\mathbb{E}_1$-\emph{self}-equivalence we have an equivalence with the opposite algebra.

    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \cref{prop:dunn_additivity}. Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
\end{example}

>>>>

Given a stratified manifold $M$, we defined the $\infty$-category of locally constant factorization algebras on it $\lcfa_M (\catC)$. We want to examine what we can say about the behavior of this $\infty$-category under collar-gluings in the manifold variable. Our discussion will be in terms of disk algebras $\alg{\disk_{/M}} (\catC)$, but using \Cref{thm:disk_alg=lcfa} there is no loss at all.

@@

\begin{corollary}\label{cor:fbar_func_discrete}
    Taking only the first part of the proof of \Cref{lem:fbar_func} it is immediate that in the setting of $\mfld[r]_{/M}$ there is also a functor
    %
    \begin{equation}
        \bar{f}: \mfld[r]_{/M} \xrightarrow{\ \ \ \ } \alg{\mathsf{Assoc^{RL}}} (\mfld[r]_{/M}),
    \end{equation}
    %
    that is an algebra.
\end{corollary}

@@

\begin{proof}[Proof of \Cref{thm:gluing_alg_disk/M}]
    The data of a collar-gluing provides open embeddings $M_0 \times \mathbb{R} \xhookrightarrow{} M_-$ and $M_0 \times \mathbb{R} \xhookrightarrow{} M_+$, where $M_-$, $M_0$ and $M_+$ have the usual meanings as in \Cref{def:collar-gluing}. This can be used to construct the cospan of restriction functors $\alg{\disk_{/M_-}} (\catC) \rightarrow \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC) \leftarrow \alg{\disk_{/M_+}} (\catC)$. Using this data we can define the pullback $\infty$-category
    %
    \begin{equation}
        \mathscr{P} := \alg{\disk_{/M_-}} (\catC) \bigtimes_{\alg{\disk_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\disk_{/M_+}} (\catC).
    \end{equation}
    %
    The further open embeddings of $M_-$, $M_0 \times \mathbb{R}$ and $M_+$ into $M$ again give rise to restriction functors that form a commutative square
    %
    \begin{equation}
        \begin{tikzcd}
            \alg{\disk_{/M}} (\catC) \arrow[r] \arrow[d] & \alg{\disk_{/M_+}} (\catC) \arrow[d] \\
            \alg{\disk_{/M_-}} (\catC) \arrow[r] & \alg{\disk_{/M_0 \times \mathbb{R}}} (\catC),
        \end{tikzcd}
    \end{equation}
    %
    which, by the universal property of the pullback, gives us a canonical functor $\rho: \alg{\disk_{/M}} (\catC) \rightarrow \mathscr{P}$. Our job is to find an inverse to this functor.

    Consider the following construction. Given the data of an object $(A_-, A_+) \in \alg{\disk_{/M_-}} (\catC) \times \alg{\disk_{/M_+}} (\catC)$ such that $A_-|_{M_0 \times \mathbb{R}} = A_+|_{M_0 \times \mathbb{R}} = : A_0$ we want to construct a functor $A: \disk_{/M} \xrightarrow{} \catC$. We do this by relying on factorization homology and the bar construction. Given $(U \xhookrightarrow{} M) \in \disk_{/M}$ we define
    %
    \begin{equation}\label{eq:def_of_A_in_proof}
        A(U) := \int_{U_-} A_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} A_0} \int_{U_+} A_+,
    \end{equation}
    %
    where $U_-$, $U_0$ and $U_+$ are defined through the inherited collar-gluing $U \xhookrightarrow{} M \xrightarrow{} [-1,1]$. Well-definition of the bar construction is provided if we have the appropriate left and right module structures on $\int_{U_-} A_-$ and $\int_{U_+} A_+$ over the associative algebra $\int_{U_0 \times \mathbb{R}} A_0$. Pushforward along the restrictions $f|_{U_-}: U_- \rightarrow \left[-1, 1\right)$ and $f|_{U_+}: U_+ \rightarrow \left(-1, 1\right]$, together with the properties of factorization homology provides these left and right module structures. Furthermore, the associative algebra object is exactly the appropriate one since consecutive restrictions commute on the nose. The above argument is essentially the statement that there is a functor
    %
    \begin{align}
        \gamma: \mathscr{P} \xrightarrow{\ \ \int \ \ } &\alg{\mfld_{/M_-}}(\catC) \bigtimes\limits_{\alg{\mfld_{/M_0 \times \mathbb{R}}} (\catC)} \alg{\mfld_{/M_+}} (\catC)\notag\\ &\xrightarrow{\ - \circ \bar{f} \ } \mathsf{Fun}(\mfld_{/M}, \alg{\mathsf{Assoc^{RL}}} (\catC)) \xrightarrow{\ \mathsf{B} \circ - \ } \mathsf{Fun}(\mfld_{/M},\catC) \xrightarrow{\ } \mathsf{Fun}(\disk_{/M}, \catC),
    \end{align}
    %
    where $\bar{f}$ is the functor from \Cref{lem:fbar_func}.

    Our first order of business is to show that $\gamma$ actually even lands in $\alg{\disk_{/M}} (\catC)$, and not just $\mathsf{Fun}(\disk_{/M}, \catC)$. Since we have expressed the construction $A = \gamma(A_-, A_+)$ functorially, we can see that $A$ will inherit the structure of an algebra from the fact that factorization homology and the bar construction are symmetric monoidal functors (see \Cref{lem:B_sym_mon} for the latter), together with \Cref{lem:fbar_func} that lends this property to $\bar{f}$. With that we have constructed a functor
    %
    \begin{equation}
        \gamma : \mathscr{P} \xrightarrow{\ \ \ \ } \alg{\disk_{/M}} (\catC).
    \end{equation}

@@

    Finally, we want to show that $\rho$ is fully faithful, i.e. we want to show that
    %
    \begin{equation}
        \begin{tikzcd}
            \mathsf{Hom}_{\alg{\disk_{/M}} (\catC)}(A, B) \arrow[r, bend left=4, "\rho"] & \mathsf{Hom}_{\mathscr{P}}((A_-, A_+), (B_-, B_+)) \arrow[l, bend left=4, "\gamma"]
        \end{tikzcd}
    \end{equation}
    %
    represents an equivalence of spaces for each $A, B \in \alg{\disk_{/M}} (\catC)$. That is, we have to do similar computations as (1) and (2) above, but now on the level of morphisms. Nothing new happens in the calculations involving restrictions that don't involve multiple pieces, since their logic essentially only depends on the properties of the bar construction when restricting. In the rest of the calculations we crucially used the collar-gluing property of factorization homology. That this property continues to hold at the morphism level is a consequence of the fact that we made sure to elevate the statement of \Cref{prop:barconst=intinterval} to the level of functors, together with the pushforward property which also holds functorially à la \Cref{rem:fh_pushforward_functorial}. Namely, these provide equivalences of functors
    %
    \begin{equation}
        \int_U - \simeq \int_{[-1,1]} (f|_U)_* - \simeq \mathsf{B} \circ (f|_U)_* = \int_{U_-} (-)_- \bigotimes\limits_{\int_{U_0 \times \mathbb{R}} (-)_0} \int_{U_+} (-)_+,
    \end{equation}
    %
    which is exactly the collar-gluing property extended to the level of morphisms.
\end{proof}

Together with \Cref{thm:disk_alg=lcfa} we immediately have the following corollary:

@@

Taking into account \Cref{cor:disk_alg=falg} together with \Cref{cor:fbar_func_discrete}, as well as the definition of factorization homology in the setting of the category $\disk[r]_{/M}$, the proof of \Cref{thm:gluing_alg_disk/M} can be seen to clearly hold even in case of ordinary factorization algebras.

@@

\begin{example}\label{ex:reproduce_lcfas_on_interval}
    With the ingredients we have introduced up to now, specifically in \Cref{ssec:lcfa_on_ints}, we can do a nontrivial check of the gluing theorem. This is because we can write a collar-gluing of the closed interval $[-1,1] \cong \left[-1,1\right) \coprod_{(-1,1)} \left(-1,1\right] \cong \mathbb{R}_{\geq 0} \coprod_{\mathbb{R}} \mathbb{R}_{\leq 0}$. We note here that we have written $\mathbb{R}_{\leq 0}$ and $\mathbb{R}_{\geq 0}$ to emphasize the maps forming the decomposition. At the level of unstructured objects these two are isomorphic (see also \Cref{rem:left_or_right_module}). For this example, the theorem says that locally constant factorization algebras on the closed interval should be given by
    %
    \begin{equation}
        \lcfa_{[-1,1]} (\catC) \simeq \lcfa_{\mathbb{R}_{\geq 0}} (\catC) \bigtimes_{\lcfa_{\mathbb{R}} (\catC)} \lcfa_{\mathbb{R}_{\leq 0}} (\catC) \simeq \mathsf{RMod} (\catC) \bigtimes_{\alg{\mathbb{E}_1} (\catC)} \mathsf{LMod} (\catC),
    \end{equation}
    %
    where the functors are the ones that forget the module. At the level of objects, this is the data of an algebra with a right module $(A, R) \in \mathsf{RMod} (\catC)$ and an algebra with a left module $(B, L) \in \mathsf{LMod} (\catC)$, such that the algebras are equal $A = B$. But this is exactly the same as the description we gave in terms of an algebra with a left and a right module, i.e. an algebra over $\mathsf{Assoc^{RL}}$, in \Cref{cor:lcfas_on_closed_int}.
\end{example}

\begin{example}\label{ex:reproduce_lcfas_on_S1}
    A highly nontrivial check of the gluing theorem is given by the circle $S^1$. Using results from \cite[prop.4.0.1]{cg2016}, namely inheritance from a covering space, \cite[sec.5.5]{ginot2015} characterizes locally constant factorization algebras on the circle $S^1$ as
    %
    \begin{equation}
        \lcfa_{S^1} (\catC) \simeq \aut (\alg{\mathbb{E}_1} (\catC)),
    \end{equation}
    %
    i.e. $\mathbb{E}_1$-algebras together with a self-equivalence. This result is not generalizable to higher spheres because it uses the technology of covering spaces. \Cref{cor:gluing_lcfas} allows us to recover this nontrivial result. To wit, the circle can be exhibited as a collar-gluing $S^1 \cong \mathbb{R} \coprod_{S^0 \times \mathbb{R}} \mathbb{R} \cong \mathbb{R} \coprod_{\mathbb{R} \sqcup \mathbb{R}} \mathbb{R}$. For locally constant factorization algebras this means that
    %
    \begin{equation}\label{eq:lcfas_on_S1_gluing}
        \lcfa_{S^1} (\catC) \simeq \lcfa_{\mathbb{R}} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \bigtimes_{\lcfa_{\mathbb{R} \sqcup \mathbb{R}} (\catC)} \alg{\mathbb{E}_1} (\catC).
    \end{equation}
    %
    Since a disjoint union is a collar-gluing we also have that $\lcfa_{\mathbb{R} \sqcup \mathbb{R}} \simeq \lcfa_{\mathbb{R}} (\catC) \times \lcfa_{\mathbb{R}} (\catC) \simeq \alg{\mathbb{E}_1} (\catC) \times \alg{\mathbb{E}_1} (\catC)$. Let's denote the restriction functors that restrict to the first and the second component of the disjoint union $\mathbb{R} \sqcup \mathbb{R}$ by $|_1$ and $|_2$ respectively. Going back to \Cref{eq:lcfas_on_S1_gluing}, the data of a locally constant factorization algebra on $S^1$ is equivalent to the data of two $\mathbb{E}_1$-algebras $A$ and $B$ such that their restrictions $A|_1 = B|_1$ and $A|_2 = B|_2$ agree. Since all of these are $\mathbb{E}_1$-algebras there are equivalences with the restrictions forming
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1 & \\
            A \arrow[rd, phantom, "\simeq", sloped, description] \arrow[ru, phantom, "\simeq", sloped, description] & & & B \arrow[lu, phantom, "\simeq", sloped, description] \arrow[ld,  phantom, "\simeq", sloped, description] \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 &                        
        \end{tikzcd}
    \end{equation}
    %
    That is we have the data of two algebras $A$ and $B$, and two equivalences from $A$ to $B$. It is standard that this data is equivalent (in one direction by composing) to the data of an $\mathbb{E}_1$-algebra with a self-equivalence.
\end{example}

\begin{example}\label{ex:lcfas_on_S^n}
    Unlike the covering space result for the circle \cite[sec.5.5]{ginot2015} which doesn't generalize to higher spheres, the gluing theorem has no such restriction. Just as for the circle, higher spheres can also be described as a collar-gluing $S^n \cong \mathbb{R}^n \coprod_{S^{n-1} \times \mathbb{R}} \mathbb{R^n}$. Thus, we can iterate the procedure from \Cref{ex:reproduce_lcfas_on_S1} to get the locally constant factorization algebras on all higher spheres. For example, for the two-sphere $S^2$ we have
    %
    \begin{equation}
        \lcfa_{\mathbb{R}^2}(\catC) \bigtimes_{\lcfa_{S^1 \times \mathbb{R}}(\catC)} \lcfa_{\mathbb{R}^2}(\catC) \simeq \alg{\mathbb{E}_2}(\catC) \bigtimes_{\alg{\mathbb{E}_1}( \aut (\alg{\mathbb{E}_1} (\catC))) } \alg{\mathbb{E}_2} (\catC),
    \end{equation}
    %
    namely, a locally constant factorization algebra on $S^2$ is equivalent to two $\mathbb{E}_2$-algebras, such that they restrict on the fattened equator to the same $\mathbb{E}_2$-algebra equipped with an $\mathbb{E}_1$-automorphism. It is nontrivial to describe this data in a simpler way as was possible for $S^1$.

@@

\begin{example}\label{ex:cylinder_mobius_band}
    In \Cref{ch:classif_defect_mfld} we will see that fiber bundles are important for the classification of some stratified manifolds. Here we will look at line bundles over the circle as a toy example, namely, the cylinder $C$ and M\"obius band $M$. The cylinder, as a trivial fiber bundle, is isomorphic to the product space $S^1 \times \mathbb{R}$. By \Cref{prop:exp_of_products_lc} together with the results of \Cref{ex:reproduce_lcfas_on_S1}, locally constant factorization algebras on it are given by $\mathbb{E}_2$-algebras together with an $\mathbb{E}_1$-self-equivalence
    %
    \begin{align}
        \lcfa_C (\catC) \simeq \aut_{\mathbb{E}_1} (\alg{\mathbb{E}_2} (\catC)).
    \end{align}

    Switching our attention to the M\"obius band $M$, we can use a similar logic as in \Cref{ex:reproduce_lcfas_on_S1} to find a collar gluing of $M$. The pieces are the same as they would be for the cylinder, namely $M_- \cong M_+ \cong \mathbb{R}^2$, and $M_0 \times \mathbb{R} \cong \mathbb{R}^2 \sqcup \mathbb{R}^2$, but they are glued differently because of the twist. Using the notation from \Cref{ex:reproduce_lcfas_on_S1} the diagram becomes
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small, column sep= small]
            & A|_1 \arrow[r, phantom, "=", description] & B|_1^{\mathsf{op_f}} \arrow[r, phantom, "\simeq", description] & B^{\mathsf{op_f}} \\
            A \arrow[ru, phantom, "\simeq", sloped, description] \arrow[rd, phantom, "\simeq", sloped, description] & & & \\
            & A|_2 \arrow[r, phantom, "=", description] & B|_2 \arrow[r, phantom, "\simeq", description] & B,
        \end{tikzcd}
    \end{equation}
    %
    where $^{\mathsf{op_f}}$ is the opposite functor in the fiber direction. Thus, instead of an $\mathbb{E}_1$-\emph{self}-equivalence we have an equivalence with the opposite algebra.

    We should remark that the fact that we can take the opposite algebra in one direction only is a consequence of the Dunn additivity of \Cref{prop:dunn_additivity}. Without it, we wouldn't be able to combine the opposite algebra in one direction with the original algebra in the other direction into a well-defined algebra in two dimensions.
\end{example}
